Comparison among doublet predictions on benchmarking datasets

### 2024-07-18 analyses/doublet-detection/exploratory-notebooks/03_compare-benchmark-results.Rmd

- `consensus_class`, which will be "doublet" if all three methods are doublet, "singlet" if all three methods are singlet, and "ambiguous" if there are any disagreements
- `consensus_call`, which will be "doublet" if _all_ methods predict "doublet," and "singlet" otherwise
- `confusion_call`, which will classify the consensus call as one of "tp", "tn", "fp", or "fn" (true/false positive/negative) based on `consensus_call`

>>>>

- `consensus_class`, which will be "doublet" if all three methods are doublet, "singlet" if all three methods are singlet, and "ambiguous" if there are any disagreements
- `consensus_call`, which will be "doublet" if _all_ methods predict "doublet," and "singlet" otherwise
- `confusion_call`, which will classify the consensus call as one of `tp`, `tn`, `fp`, or `fn` (true/false positive/negative) based on `consensus_call`
